---
output: html_document
editor_options: 
  chunk_output_type: inline
---


# Initial creation of package and repository

```{r}
root_dir = "~/ELViS"
dir.create(root_dir,recursive=T)
knitr::opts_knit$set(root.dir = root_dir)
setwd(root_dir)
print(knitr::opts_knit$get("root.dir") )
getwd()
library(devtools)

# use_r_vscode = function(fn,root=root_dir){
#     system(paste0("code -r ",root,"/R/",fn))
# }
# 
# use_r_vscode("test.R")
# # create_package()
```

```{r}

use_git() # error happens but no worries. This has to be done once before use_fit_config call
# make it git repository
use_git_config(scope = c("project"),user.name="JYLeeBioinfo",user.email="jlee307@uthsc.edu")
use_git()

# add license
use_mit_license()

# usethis::create_github_token()
# firefox does not work, then paste the url into chrome
# it is useful since they have set some preset for scopes

# require latest git
# create gitbub repo
gitcreds::gitcreds_set()
# use_github(private = TRUE)



```

remove NAMESPACE and 

```{r}
document()

use_git()
# system("cd ..;git push")
# 
# getwd()

```



```{r}
sync_namespace_to_description <- function(namespace_file = "NAMESPACE",force_rewrite=FALSE,biocViews_type="software",bump_ver_which=NULL) {
  # Read the NAMESPACE file
  lines <- readLines(namespace_file)
  
  # Extract package names from 'import' and 'importFrom' statements
  import_lines <- grep("^import\\(|^importFrom\\(", lines, value = TRUE)
  
  # Capture package names
  packages <- unique(gsub("^import\\(|^importFrom\\(|\\)$|,.+$", "", import_lines))
  
  # Load `desc` and `usethis`
  require(desc)
  require(usethis)
  
  # Ensure the DESCRIPTION file exists
  run_license_addition = FALSE
  if((!file.exists("DESCRIPTION"))|force_rewrite){
    usethis::use_description()
  
    # Read the DESCRIPTION file
    desc_file <- desc::description$new("DESCRIPTION")
    
    desc_file$set_version("0.99.0")
    desc_file$set("VignetteBuilder", "knitr")
    desc_file$set("biocViews", biocViews_type)
    desc_file$set("LazyData", "false")
    desc_file$del_author()
    run_license_addition = TRUE
  }else{
    desc_file <- description$new(file = "DESCRIPTION")
    if(!is.null(bump_ver_which)){
      desc_file$bump_version(which=bump_ver_which)
    }
  }
  
  
  
  # update package list
  desc_file$del_deps()
  for (pkg in packages) {
    if (!desc_file$has_dep(pkg)) {
      desc_file$set_dep(pkg, "Imports")
    }
  }
  
  
  # Save the changes to DESCRIPTION
  desc_file$write("DESCRIPTION")
  if(run_license_addition){
    use_mit_license()
  }
  
  
  message("DESCRIPTION file has been updated with packages from NAMESPACE.")
}
```

```{r}

setwd(root_dir)
usethis::use_description()
desc_file <- desc::description$new("DESCRIPTION")

# desc_file$bump_version("0.0.9")
desc_file$bump_version(which = 3)

setwd(root_dir)
desc2 <- description$new(file = "DESCRIPTION")


```


```{r}
setwd(root_dir)
sync_namespace_to_description()
use_git()
```



```{r}
## If needed
# remotes::install_github("lcolladotor/biocthis")

## Create a GitHub Actions (GHA) workflow that is Bioconductor-friendly
biocthis::use_bioc_github_action()
usethis::use_github_action("check-standard.yaml")
use_git()

```

```{bash}
cd ..
git commit
git push
cd -
```

now go to Clone_Package_Remote_Server.rmd and execut git pull











# When getting the latest copy available on github

```{bash}
cd ..
git pull
cd -
```



# create vignette

```{r}
usethis::use_vignette("ELViS_Toy_Example")
```




# after making changes

```{r}
root_dir = dirname(getwd())
dir.create(root_dir,recursive=T)
knitr::opts_knit$set(root.dir = root_dir)
setwd(root_dir)
print(knitr::opts_knit$get("root.dir") )
getwd()
library(devtools)
```





```{r}
# setwd(root_dir)
document() # modify NAMESPACE according to roxygen notatio in R scripts
sync_namespace_to_description() # modify DESCRIPTION accordint to NAMESPACE file
use_git()
```


```{r}
# if use_git() throws error
use_git_config(scope = c("project"),user.name="JYLeeBioinfo",user.email="jlee307@uthsc.edu")
use_git()

```


```{r}
# DESCRIPTION_add_author = function(...){
#   desc_file <- description$new(file = "DESCRIPTION")
# desc_file$add_author(...)
# desc_file$write("DESCRIPTION")
#   
# }

# arg_to_string <- function(arg) {
#   deparse(substitute(arg))
# }

DESCRIPTION_action = function(func,...){
  func_str = (gsub('"','',deparse(substitute(func))))
  desc_file <- description$new(file = "DESCRIPTION")
  desc_file[[func_str]](...)
  desc_file$write("DESCRIPTION")
}
```


# build test

```{r}
document()
# pick terms from https://bioconductor.org/packages/devel/BiocViews.html
target_biocviews =
  c("CopyNumberVariation"
    ,"Coverage"
    ,"GenomicVariation"
    ,"BiomedicalInformatics"
    ,"Sequencing"
    ,"Normalization"
    ,"Visualization"
    ,"Clustering")

setwd("..");sync_namespace_to_description()
# setwd("..");sync_namespace_to_description(biocViews_type=paste(target_biocviews,collapse = ", "),force_rewrite = TRUE)

# setwd("..")
DESCRIPTION_action(
  set,
  "Depends", "R (>= 4.3)"
)

# setwd("..");DESCRIPTION_action(
#   set,
#   "Depends", "R (>= 2.10)"
# )

# importing packages should be less than 20 to prevent any notes
# setwd("..")
pkgs_suggest = c("reticulate","Rsamtools","BiocManager")
DESCRIPTION_action(
  set_list,
  "Suggests",
  paste0("\n",paste(pkgs_suggest,collapse=",\n"))
  )
# setwd("..")
DESCRIPTION_action(
  set,
  "BugReports", "https://github.com/hyochoi/ELViS/issues"
)
# setwd("..")
DESCRIPTION_action(
  set,
  "URL", "https://github.com/hyochoi/ELViS"
)

# setwd("..")
DESCRIPTION_action(
  add_author,
  given = "Hyo Young",family = "Choi",email = "hyoyoung.choi@uthsc.edu",role = c("aut"))

DESCRIPTION_action(
  add_author,
  given = "Jin-Young",family = "Lee",email = "jlee307@uthsc.edu",role = c("aut","cre"),orcid = "0000-0002-5366-7488")

DESCRIPTION_action(
  add_author,
  given = "D. Neil",family = "Hayes",email = "Neil.Hayes@uthsc.edu",role = c("aut","fnd"))

# â¯ checking data for ASCII and uncompressed saves ... WARNING
#     Warning: package needs dependence on R (>= 2.10)

# library(BiocCheck)
setwd("../../testRpackage/asset/bioccheck/BiocCheck");load_all()
setwd("..");BiocCheck()
check()
# setwd("..")
  BiocCheck::BiocCheck(
      # dir('check', 'tar.gz$', full.names = TRUE),
      `quit-with-status` = TRUE,
      `no-check-R-ver` = TRUE,
      `no-check-bioc-help` = TRUE
  )
  
use_git()
```


# find and remove unused packages
```{r}

library(devtools)
load_all()

sessn = sessionInfo()
loaded_packages <- sessn$otherPkgs
package_names <- unique(c(names(sessn$otherPkgs),names(sessn$loadedOnly)))

package_names



package_name <- "ELViS"  # replace with actual package name

# List all objects in the package namespace
all_objects <- ls(getNamespace(package_name))

# Filter out only functions
package_functions <- all_objects[sapply(all_objects, function(x) is.function(get(x, envir = getNamespace(package_name))))]

# Print the list of functions
print(package_functions)


codetools::findGlobals(gene_cn_heatmaps,
                       merge = FALSE)
find("makeGRangesFromDataFrame")

used_globals =
  package_functions %>% 
  lapply(\(fn){
    codetools::findGlobals(fn,
                       merge = FALSE)$functions

  }) %>% unlist %>% unique

source_global = 
  used_globals %>%
  lapply(find) %>%
  unlist

source_global = source_global %>% unique %>% gsub("^package:","",.) %>% sort

imported_packages = 
read.table("../NAMESPACE")$V1 %>%
  grep("import",.,value=TRUE) %>%
  str_split("[)(,)]") %>%
  sapply(\(x) x[2]) %>% unique

setdiff(imported_packages,source_global)

used_globals

unused_packages <- package_names[!sapply(package_names, function(pkg) {
  any(grepl(paste0("^", pkg, "::"), used_globals))
})]

loaded_packages <- sessionInfo()$otherPkgs



```




```{bash}
cd .. 
git pull
```



```{bash}
cd ..
git commit
git push
cd -
```


```{bash}
cd ..
git add -A
git commit
git push -f
```


# post push testing
 - install into new conda environment with new base R
 - if successful, run github action by changing the workflow file to something other





# run github action locally
 - https://medium.com/@debasishkumardas5/running-github-actions-locally-a-complete-guide-for-windows-mac-and-linux-users-34c45999c7cd

 - after docker installation, run following to add yourself to docker group

 - `sudo usermod -aG docker $USER`



```{bash}

export PATH="${PATH}":~/bin # path to act executable
cd ..
act
cd -

```



